\pagestyle{plain}

\addcontentsline{toc}{section}{Acknowledgements}
{\Large Acknowledgments}\\
\hrule

No project such as this one could have come into existence without the effort from many other people. Here, I would like to acknowledge those who have given up some of their time and expertise to help me put this project together, from the start where it was a seemingly ambitious idea, to now where everything actually works. The success of this project can only be due to the support structure that I have, and for that I am truly grateful.

I'd like to firstly thank my project supervisor, Prof. Peter Martinez, for his guidance in the project as well as in the field of space science in general. It is refreshing to work with an expert in the field willing to recognise and explore others' ideas for the better of the project.

I'd like to thank Justin Pead from the UCT's Whitelab for facilitating all the extraordinary electrical and mechanical requests that came about from the project. I am thankful for the guidance he has given me in many projects during my undergraduate degree.

I'd like to thank the members of the SpaceLab, in which I worked on this project, for checking up on me almost everyday. The SpaceLab was an incredible place in which to work and everyone was supportive of the work that I was doing, ready to get up and help me out whenever I needed it.

I'd like to thank my classmates from all corners of the electrical department. I learnt from them that this degree was not one walked alone, and this was a collective realisation among us all. I'd like to thank all of those who sacrificed some of their own achievement to carry us through the workload and the difficulty of the degree. I'd also like to thank my close friends outside of the Engineering faculty. It's tough dealing with someone who wants to talk geek at all hours of the day.

I'd like to thank Martin from ProtoLink3D for the stupendously generous sponsorship of all the 3D manufacturing for the project. Lack of his and his company's support would have resulted in the project not being completed and his help and generosity came timeously in terms of the development of the model.

Finally, I'd like to thank my family. After all that we have been through, we have still remained strong, close and supportive of all the things that we do. Thank you to my sisters, Emilie and Caitlin, for following me on this little journey that has been this semester. Thank you to my Mom and my Dad for the unconditional support in all areas technical, emotional and material. I am truly blessed to have the wisest group of people that I know as my family.